\section{Equilibrium Comparison between PRMs}
\label{sec:theoretic}

This section establishes that profit reallocation mechanisms on trees expand equilibrium trade events compared with the baseline mechanism. As there may be multiple equilibria, we fix the simplified perfect Bayesian equilibrium $(\tbmp^*, \tbms^*)$ satisfying~\eqref{SE:transform}, constructed by the backward induction of \cref{lem:simplify-sell,cor:simplify-buy}.
Ties in each $\argmax$ are resolved by choosing the \emph{smallest} element. This tie-breaking rule is independent of $\pi$, thus does not provide advantages to some specific PRM. We impose two additional assumptions:

\begin{assumption}[Positivity]
\label{asp:posi}
$\Pr_{\bmv \sim \calF}[v_i > 0] = 1$ for all $i \in \calI$.
\end{assumption}

\begin{assumption}[Homogeneity]
\label{asp:homo}
Under \cref{asp:markov}, for all $\alpha, w, v > 0$ and $i \in \calI \setminus \{r\}$: $F_i(\alpha v \mid \alpha w) = F_i(v \mid w)$.
\end{assumption}

Positivity says that a data product is always worth more than the cost of producing it. Homogeneity is a scaling property common in economic modeling~\citep[\S6.2]{AGT:nisan_algorithmic_2007}, \citep[\S3.2.3]{DSGE}; it holds whenever the value of the output is proportional to the value of the input.

Given a simplified strategy profile $(\tbmp, \tbms)$, we define the \emph{trade event} for trade $j \in \calI \setminus \{r\}$ as
\begin{equation}
\label{eq:trade-event}
E_j(\tbmp, \tbms) \;\coloneqq\; \big\{\bmv \in \calV : \ts_j(v_j) \ge \tp_j(v_{\Parent(j)})\big\},
\end{equation}
\ie, the set of valuation profiles under which player $j$ is willing to buy at the price her parent offers.
%  (the first-stage condition for trade $j$, independent of whether upstream trades succeed). Whenever a mechanism $\pi^k$ admits the equilibrium $(\tbmp^{k,*}, \tbms^{k,*})$, its trade event is $E_j(\tbmp^{k,*}, \tbms^{k,*})$.

% Homogeneity endows the equilibrium with a scaling structure that is the workhorse of our comparisons: equilibrium strategies are linear in valuations, and any trade whose seller collects only a one-shot payment has a mechanism-independent threshold (the \emph{homogeneity scaling lemma}, \cref{lem:scaling} in \cref{sec:omitted-proofs}).


\subsection{Local Comparison between Mechanisms}
\label{subsec:partial}

We first compare two PRMs that reallocate profit differently along a single trade, where one rewards the upstream seller more from downstream resale than the other. This relation is inherently asymmetric, so we phrase it as \emph{local dominance} rather than a symmetric difference.

\begin{definition}[Local Dominance]
\label{def:local-diff}
For a non-root player $j \in \calI \setminus \{r\}$, let $i \coloneqq \Parent(j)$. A PRM $\pi^1$ \emph{locally dominates} another PRM $\pi^2$ \emph{at trade $j$} if:
\begin{enumerate}[label=(\alph*),left=0em]
\item $\pi^1(m, k) = \pi^2(m, k)$ for all $m \in \calI \setminus \{r\}$ and all $k \in \calI \setminus \{i\}$.
\item $\pi^1(j, i) \le \pi^2(j, i)$: player $i$'s one-shot profit from trade $j$ is weakly smaller under $\pi^1$.
\item $\pi^1(m, i) \ge \pi^2(m, i)$ for all $m \in \Desc(j)$: player $i$'s reallocated profit from downstream trades is weakly larger under $\pi^1$.
\item $\pi^1(m, k) = \pi^2(m, k) = \pi^0(m, k)$ for all $k \in \Path(i)$ and all $m \in \calI \setminus \{r\}$: both mechanisms use baseline mechanisms for all strict ancestors of $i$.
\item $\pi^1(m, i) = \pi^2(m, i)$ for all $m \notin \Subtree(j)$: player $i$'s reallocation is unchanged outside $\Subtree(j)$.
\end{enumerate}
That is, relative to $\pi^2$, the dominating mechanism $\pi^1$ shifts $i$'s reward away from its one-shot payment on trade $j$ toward the downstream resale within $\Subtree(j)$, leaving everything else fixed.
\end{definition}

\begin{restatable}{theorem}{thmPartial}
\label{thm:partial}
Let $\calF$ satisfy \cref{asp:markov,asp:posi,asp:homo}. Let $\pi^1$ locally dominate $\pi^2$ at trade $j$ (\cref{def:local-diff}). Let $(\tbmp^{k,*}, \tbms^{k,*})$ be the equilibrium under $\pi^k$ for $k \in \{1,2\}$. Then:
\begin{enumerate}
\item $E_m(\tbmp^{1,*}, \tbms^{1,*}) = E_m(\tbmp^{2,*}, \tbms^{2,*})$ for all $m \in \calI \setminus \{r\}$ with $m \neq j$.
\item $E_j(\tbmp^{2,*}, \tbms^{2,*}) \subseteq E_j(\tbmp^{1,*}, \tbms^{1,*})$.
\end{enumerate}
\end{restatable}

\emph{Proof Sketch.}
Write $i \coloneqq \Parent(j)$. The two mechanisms differ only in how they reward $i$, and only from within $\Subtree(j)$ (conditions (a)--(e)); every other reallocation is fixed. We show each trade event $E_m$ with $m\neq j$ is unchanged, then analyze trade $j$.

\emph{(i) $m\notin\Subtree(i)\cup\Path(i)$ and (ii) $m\in\Desc(j)$.} These equilibria are computed inside subtrees whose \emph{internal} profit reallocations are same between $\pi_1$ and $\pi_2$, so their equilibrium strategies, hence $E_m$, are identical.

\emph{(iii) Sibling trades $m\in\Subtree(c)$, $c\in\Children(i)\setminus\{j\}$.} By subtree decomposition (\cref{lem:subtree-decomp}), $i$'s optimal price to $c$ and equilibrium strategy within $\Subtree(c)$ depend only on the reallocations within $\Subtree(c)$ as well as the reallocations from $\Subtree(c)$ to $i$. While condition (e) ensures that these reallocations are same between $\pi_1$ and $\pi_2$. Similarly, $E_m$, are identical.


\emph{(iv) Path trades $m\in\Path(i)\cup\{i\}$.} Both $\pi_1$ and $\pi_2$ use the baseline mechanism along this path (condition (d)), so the seller collects only her \emph{one-shot} payment. We first derive a homogeneity scaling lemma (\cref{lem:scaling} in \cref{sec:omitted-proofs}): $\ts_m(v_m)$ is linear in $v_m$, and hence $E_m = \{\bmv : v_m/v_{\Parent(m)} \ge \tau_m\}$ with $\tau_m$ depending only on $F_m$. Therefore, $E_m$ is identical between $\pi_1$ and $\pi_2$.

\emph{Trade $j$.} By (ii), all strategies within $\Subtree(j)$ are unchanged, so $\ts_j$ is identical between $\pi_1$ and $\pi_2$. Only the price $\tp_j$ may differ. Split $i$'s gain $G^{(j)}_i = r_i + d_i$ into the one-shot revenue $r_i$ from $j$ and the reallocated revenue $d_i$ from $\Desc(j)$. Under the dominating $\pi^1$, $i$'s one-shot revenue is smaller (condition (b)) and its reallocated revenue is larger (condition (c)): $i$ earns \emph{less} directly from $j$ and \emph{more} from what $j$ resells. As the reallocated revenue accrues only when $j$ buys and then resells, $i$ is incentivized to induce more downstream trade, and its only lever is to \emph{lower} $\tp_j$, admitting more willingness for player $j$ to buy, and resulting $E_j(\tbmp^{2,*}, \tbms^{2,*}) \subseteq E_j(\tbmp^{1,*}, \tbms^{1,*})$.
\qed

\subsection{Comparison with Baseline Mechanism}
\label{subsec:global}

The local comparison result (\cref{thm:partial}) serves as the building block for a global comparison between any PRM and the baseline mechanism.

\begin{restatable}{theorem}{thmGlobal}
\label{thm:global}
Let \cref{asp:markov,asp:posi,asp:homo} hold.
Let $\pi^0$ be the baseline mechanism (\cref{def:baseline}) and $\pi$ be any feasible PRM satisfying \cref{def:prm}. Denote by $(\tbmp^{0,*}, \tbms^{0,*})$ and $(\tbmp^*, \tbms^*)$ the equilibria under $\pi^0$ and $\pi$, respectively. Then $E_j(\tbmp^{0,*}, \tbms^{0,*}) \subseteq E_j(\tbmp^*, \tbms^*)$ for all $j \in \calI \setminus \{r\}$.
\end{restatable}

\input{Contents/Statements/prf_thm_global}

The expansion of every trade event translates directly into a social welfare improvement.

\begin{corollary}[Welfare Improvement]
\label{cor:welfare}
Let \cref{asp:markov,asp:posi,asp:homo} hold and let $\pi$ be any \emph{budget-balanced} PRM, \ie, $\sum_{i \in \Path(j)} \pi(j,i) = 1$ for every $j \in \calI \setminus \{r\}$, with equilibrium $(\tbmp^*, \tbms^*)$; let $(\tbmp^{0,*}, \tbms^{0,*})$ be the equilibrium under the baseline mechanism $\pi^0$. Then $\pi$ weakly improves expected social welfare over $\pi^0$:
\[
\bbE_{\bmv \sim \calF}\big[\SW(h(\tbmp^*, \tbms^*; \bmv); \bmv)\big] \;\ge\; \bbE_{\bmv \sim \calF}\big[\SW(h(\tbmp^{0,*}, \tbms^{0,*}; \bmv); \bmv)\big].
\]
\end{corollary}

The proof, deferred to \cref{sec:omitted-proofs}, rests on a simple identity: under budget balance the monetary transfers cancel, so welfare equals the total realized valuation, $\SW(h;\bmv) = \sum_{i} y_i v_i$. By \cref{thm:global} each indicator $y_i$ is weakly larger under $\pi$ than under the baseline $\pi^0$, and positivity ($v_i > 0$) turns this into a weakly larger welfare.
